\chapter{Introduction}\label{ch:introduction}

\paragraph{The Future of Vehicle Automation} 

In recent years, a big emphasis has been on the development of autonomous or semi-autonomous ground vehicles. It comes as no surprise considering it is no longer a question of will this technology be implemented, but rather when.\todo{citation needed} The benefits of autonomous vehicle integration can be considered invaluable. Currently 90\% of motor vehicle fatalities are estimated to be due to human errors \todo{citation needed}, meaning that vehicle automation could result in substantial decrease of accidents. Furthermore, depending on the percentage of autonomous vehicles on the roads, a research concluded, a drastic reduction in traffic and congestions can occur.\todo{citation needed} 

Nonetheless, there is still much work to be done in perfecting the control as well as the odometry of autonomous ground vehicles. 


\section{Examples}
You can also have examples in your document such as in example~\ref{ex:simple_example}.
\begin{example}{An Example of an Example}
  \label{ex:simple_example}
  Here is an example with some math
  \begin{equation}
    0 = \exp(i\pi)+1\ .
  \end{equation}
  You can adjust the colour and the line width in the {\tt macros.tex} file.
\end{example}

\section{How Does Sections, Subsections, and Subsections Look?}
Well, like this
\subsection{This is a Subsection}
and this
\subsubsection{This is a Subsubsection}
and this.

\paragraph{A Paragraph}
You can also use paragraph titles which look like this.

\subparagraph{A Subparagraph} Moreover, you can also use subparagraph titles which look like this\todo{Is it possible to add a subsubparagraph?}. They have a small indentation as opposed to the paragraph titles.

\todo[inline,color=green]{I think that a summary of this exciting chapter should be added.}
